TODO: A Survey of StarCraft AI Techniques

### 2012-09-20 survey.tex
minor corrections

% HARD-CODED:
Hard-coded approaches have been extensively used in commercial RTS games. The most common approaches make use finite state machines (FSM) \cite{FSM_AIGameProgWisdom2003} in order to let the AI author hard-code the strategy that the AI will employ. The idea behind FSMs is to decompose the AI behavior into easily manageable states, such as ``attacking'', ``gathering resources'' or ``repairing'' and establish the conditions that trigger transitions between them. Commercial approaches also include Hierarchical FSMs, in which FSMS are composed hierarchically. These hard-coded approaches have achieved a significant amount of success, and, as we will discuss later, have also been used in many academic RTS AI research systems, as discussed in Section \ref{sec:bot}. However, strategic decision making is a hard problem, and these hard-coded approaches struggle to encode dynamic, adaptive behaviors.

@@

% MACHINE LEARNING:
Concerning machine learning-based approaches, Weber and Mateas \cite{WeberCig09} proposed ``a data mining approach to strategy prediction'' and performed supervised learning (from buildings features) on labeled StarCraft replays. Dereszynski et al. \cite{HMMstrat_RTS_AIIDE11} used HMM to learn the transition probabilities of sequences of constructions and kept the most probables to produce probabilistic behavior models (in StarCraft). Synnaeve and Bessi\`{e}re \cite{SynnaeveOpeningCig11} extended \cite{WeberCig09} and used a Bayesian semi-supervised (labeling based on EM clustering considering appropriate features) model to learn from replays and predict openings (early game strategies) from StarCraft replays. Then \cite{SynnaeveAIIDE11}, they presented an unsupervised learning Bayesian model for tech-tree prediction, still using replays.

@@

{\color{blue}
[This is a preliminary list of open questions, derived from the Skype call on July 19. Some work is still required to turn this into the final list]

There are a set of problems that are either solved in RTS games (path-finding), or for which we have very good solutions (micro management). But there are features that are not exhibited by any of the current Starcraft playing bots. For example, current bots are incapable of coming up on their own with tactical moves such as unit drops. Some bots do drops, but only if this is hard-coded; no bot has the capability of reasoning about all the possible moves available, and discovering that doing a drop is the best thing to do right now. This is related to the lack of real-time adversarial planning techniques that scale up to RTS games. Similarly, current bots do not exhibit adaptation to opponent strategies. Some switch between different build-orders, but do not fully adapt their strategy. No bot is capable of observing the opponent and autonomously come up with a good plan (from scratch) to counter the opponent strategy.

In general, this is a list of open problems:

\begin{itemize}
\item Adaptation to opponent
\item Learning (from opponent, from traces or from mistakes)
\item Scalability: this includes:
\begin{itemize}
\item a) how to scale up existing algorithms for adversarial domains like game tree search or others, and 
\item b) multi-scale planning/reasoning, how to integrate control, tactics and strategy together (e.g. how to interface them).
\end{itemize}
\item Adversarial real-time planning and scheduling under uncertainty with resources: this basically includes three general unsolved AI problems:
\begin{itemize}
\item Adversarial planning under real-time constraints (there is some work on this area to be presented this year in AIIDE)
\item Adversarial planning under uncertainty 
\item Planning with resources (there exist planning algorithms that handle resources, like GRT-R, but cannot scale up to the size of problems needed for e.g. Starcraft)
\end{itemize}
\item How to exploit and incorporate domain knowledge: we know how to incorporate some aspects of domain knowledge (e.g. build orders), but, in general, how to incorporate some forms of domain knowledge into algorithms for RTS games is still an open problem. For example, standard techniques to encode strategies for other forms of games, like Behavior Trees, are hard to deploy in RTS games. 
\end{itemize}
}

>>>>

% HARD-CODED:
Hard-coded approaches have been extensively used in commercial RTS games. The most common approaches use finite state machines (FSM) \cite{FSM_AIGameProgWisdom2003} in order to let the AI author hard-code the strategy that the AI will employ. The idea behind FSMs is to decompose the AI behavior into easily manageable states, such as ``attacking'', ``gathering resources'' or ``repairing'' and establish the conditions that trigger transitions between them. Commercial approaches also include Hierarchical FSMs, in which FSMS are composed hierarchically. These hard-coded approaches have achieved a significant amount of success, and, as we will discuss later, have also been used in many academic RTS AI research systems, as discussed in Section \ref{sec:bot}. However, strategic decision making is a hard problem, and these hard-coded approaches struggle to encode dynamic, adaptive behaviors.

@@

% MACHINE LEARNING:
Concerning machine learning-based approaches, Weber and Mateas \cite{WeberCig09} proposed ``a data mining approach to strategy prediction'' and performed supervised learning (from buildings features) on labeled StarCraft replays. Dereszynski et al. \cite{HMMstrat_RTS_AIIDE11} used HMM to learn the transition probabilities of sequences of constructions and kept the most probables to produce probabilistic behavior models (in StarCraft). Synnaeve and Bessi\`{e}re \cite{SynnaeveOpeningCig11} used the dataset of \cite{WeberCig09} and presented a Bayesian semi-supervised model to learn from replays and predict openings (early game strategies) from StarCraft replays. The openings are labeled by EM clustering considering appropriate features. Then in \cite{SynnaeveAIIDE11}, they presented an unsupervised learning Bayesian model for tech-tree prediction, still using replays.

@@

{\color{blue}
Here, describe what is left to be done.
}
